Large scale exposure and risk from pesticides in small streams

### 2016-09-30 article.tex
second draft (with already minor comments from ralf)

Small water bodies (SWB) comprise a major fraction of streams \citep{nadeau_hydrological_2007}
%needs a definition here!
, accommodate a higher proportion of biodiversity compared to larger freshwater systems \citep{davies_comparison_2008, biggs_report_2014} and play an important role in recolonization of disturbed downstream reaches \citep{liess_analyzing_2005, orlinskiy_forested_2015}.
However, SWB might be also at high risk of pesticide contamination from adjacent agricultural areas and lower dilution potential \citep{schulz_field_2004,liess_determination_1999}.
Meta-analyses using data from studies with a few sites reported higher pesticide pollution in smaller streams compared to bigger streams \citep{stehle_pesticide_2015,schulz_field_2004}.
Especially, compounds from agricultural use show seasonal rain-event-driven short term peak concentrations in SWB \citep{wittmer_significance_2010}.
Despite their biological relevance and potential pesticide exposure, only a small fraction of studies were conducted on pesticide pollution of SWB, with only few large scale studies \citep{lorenz_specifics_2016}. 
Moreover, it is currently unknown how precipitation might influence measured pesticide concentrations in national monitoring programs.

>>>>

Small water bodies (SWB) comprise a major fraction of streams \citep{nadeau_hydrological_2007}
%needs a definition here!
, accommodate a higher proportion of biodiversity compared to larger freshwater systems \citep{davies_comparison_2008, biggs_report_2014} and play an important role in recolonization of disturbed downstream reaches \citep{liess_analyzing_2005, orlinskiy_forested_2015}.
However, SWB might be also at high risk of pesticide contamination from adjacent agricultural areas and lower dilution potential \citep{schulz_field_2004,liess_determination_1999}.
Meta-analyses using data from studies with a few sites reported higher pesticide pollution in smaller streams compared to bigger streams \citep{stehle_pesticide_2015,schulz_field_2004}.
Despite their biological relevance and potentially higher pesticide exposure, a recent analysis of pesticide studies showed that a disproportionally small fraction of studies were conducted in SWB, and these were largely limited to a few sites \citep{lorenz_specifics_2016}. COnse
Moreover, it is currently unknown how precipitation might influence measured pesticide concentrations in national monitoring programs.
Especially, compounds from agricultural use show seasonal rain-event-driven short term peak concentrations in SWB \citep{wittmer_significance_2010}.
